\documentclass[10pt]{exam}
\printanswers
\usepackage{epsfig,amssymb}
\usepackage{xcolor}
\definecolor{darkred}{rgb}{0.5,0,0}
\definecolor{darkgreen}{rgb}{0,0.5,0}
\usepackage{hyperref}
\usepackage{fullpage}
\usepackage{tikz}
\pagestyle{empty} 
\usepackage{listings}
\setlength{\parindent}{0pt} %
\setlength{\parskip}{.25cm}
\newcommand{\comment}[1]{}
\boxedpoints
\addpoints
\usepackage{amsmath}
\usepackage{algorithm2e}
\usepackage{url}
\usepackage{enumitem}
\usepackage{graphics}

\pagestyle{headandfoot}
\firstpageheader{\Large CSCE 235}{{\Large Assignment 1}}{\Large Spring 2026}

\begin{document}

\hrule

\vspace{.50cm} Name
\vspace{.50cm} \rule{4in}{.001in} \hfill 
\\ NUID \rule{4.3in}{.001in}
\vspace{.50cm}

\textbf{Instructions} Follow instructions \emph{carefully}; failure to do so will result in points being deducted. You may write or type out your answers. Be sure to show sufficient work to justify your answer(s).


\begin{questions}

\question[6] Determine if each of the following sentences is a proposition. Justify your answer.
\begin{parts}
    \part The number 17 is a prime number.
    \part $5 + 8 = 12$
    \part Close the door.
\end{parts}

\begin{solution}
    Enter your solution here:
\end{solution}

\question[12] Let the following propositions be defined as:
\begin{itemize}
  \item $d$: It's Valentine's Day.
  \item $e$: You go on a Valentine’s Day excursion.
  \item $a$: You eat chocolate and ice cream.
\end{itemize}

Express each of these compound propositions as an English sentence.

\begin{parts}
\part $ d \rightarrow a $
\part $ \neg e \rightarrow a $
\part $(d \rightarrow e) \wedge (d \rightarrow a)$
\part $(a) \leftrightarrow (d \wedge e)$
\end{parts}

\begin{solution}
    Enter your solution here:
\end{solution}

\question[6] Let the following propositions be defined as:
\begin{itemize}
  \item $w$: You wore your winter coat.
  \item $v$: You visited an ice sculpture garden.
  \item $d$: You drank hot cocoa.
\end{itemize}

Write these propositions using w, v, and d and logical connectives (including negations).
\begin{parts}
    \part If you visited an ice sculpture garden, then you wore your winter coat and drank hot cocoa.
    \part If you didn't wear your winter coat, then you didn't visit the ice sculpture garden.
\end{parts}

\begin{solution}
    Enter your solution here:
\end{solution}

\question[16] Show that the following conditional statement is a tautology by using a truth table.
\begin{parts}
\part $\left [ a \wedge  (a \rightarrow b) \right ] \rightarrow b$
\part $(a \wedge b) \rightarrow (b \rightarrow a)$
\part $\left[(a \lor b) \land (a \rightarrow c) \land (b \rightarrow c) \right] \rightarrow c$
\part $\left[ \neg a \wedge (a \vee b)\right] \rightarrow b$
\end{parts}

\begin{solution}
    Enter your solution here:
\end{solution}

\question[16] Prove by logical equivalences (without using a truth table) the following is a tautology. To get full credit, you must state which logical equivalences you used in each step.

\begin{parts}
\part $\left [ a \wedge  (a \rightarrow b) \right ] \rightarrow b$
\part $(a \wedge b) \rightarrow (b \rightarrow a)$
\part $\left[(a \lor b) \land (a \rightarrow c) \land (b \rightarrow c) \right] \rightarrow c$
\part $\left[ \neg a \wedge (a \vee b)\right] \rightarrow b$
\end{parts}

\begin{solution}
    Enter your solution here:
\end{solution}

\question[8] Show that the following are logically equivalent without using a truth table. To get full credit, you must state which logical equivalences you used in each step.

\begin{parts}
\part $\neg a \rightarrow (b \rightarrow c) \equiv b \rightarrow (a \vee c)$
\part $\neg (\neg a \wedge b) \wedge (a \vee b) \equiv a$
\end{parts}

\begin{solution}
    Enter your solution here:
\end{solution}

\end{questions}

\end{document}